---
title: "Assigment - Naive Bayes DIY"
author:
  - Lars Bunnik - Author
  -  - Reviewer
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---

```{r}
library(tidyverse)
library(tm)
library(caret)
library(wordcloud)
library(e1071)
```
---

Choose a suitable dataset from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train your own Naive Bayes model. Follow all the steps from the CRISP-DM model.


## Business Understanding
The dataset that is going to be used to train and test the Naive Bayes model is the "Fake news" dataset. By training the predictive NB model which words in the titles are more likely to suggest fake news and which words aren't we test how accurate the model can predict if the article is actually fake news or if it is not.

## Data Understanding
#The first step is to look at what data we have.

```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/NB-fakenews.csv"
rawDF <- read_csv(url)

head(rawDF)
```


```{r}
#In the table there are numerous colomns that we won't use. We only need the "title" and the "label" columns. The title is the metric we use to predict if the article is reliable or not and the lable actually tells us if the article is 0 (reliable) or 1 (unreliable). So we clean the id, author and text columns.

cleanDF <- rawDF[c(-1,-3, -4)] %>% na.omit
head(cleanDF)

#the variable "label" now is of class "dbr". As it indicates whether the title belongs to the category 0: reliable or 1: unreliable we should convert it into a factor with the values "Reliable" and "Unreliable":

cleanDF$label <- cleanDF$label %>% factor
cleanDF$label <- factor(cleanDF$label, levels = c("0", "1"), labels = c("Reliable", "Unreliable")) %>% relevel("Reliable")
levels(cleanDF$label)
class(cleanDF$label)
col_order <- c("label", "title")
cleanDF <- cleanDF[, col_order]
cleanDF

## Data Preparation
text and code here

## Modeling
text and code here

## Evaluation and Deployment
text and code here

reviewer adds suggestions for improving the model
